Cryptographic assurance of secrecy and fairness in voting

### 2012-12-07 paper/paper.tex
italicize more pretas

\pv\ \cite{preta} also aims to offer a familiar, in-person voting experience while providing cryptographic assurance of
a fair election.

@@

The paper ballot form in \pv\ consists of two separable sides.
The left-hand side lists the candidates in permuted order.
A mark on the right-hand side in an initially empty slot adjacent to a candidate indicates a vote for that candidate.
In addition to the recorded vote, the right-hand side also includes the \term{onion}, an encryption of the ballot's particular candidate permutation.
See Figure \ref{fig:preta} for a depiction of the ballot form.

@@

Once all votes have been cast and recorded, the election authority mixes, decrypts, and tallies the votes to determine the winners while maintaining ballot secrecy.
Mixing the encrypted votes before or during the decryption process (depending on the \pv\ variant) ensures the votes remain anonymous -- even to the officials performing the encryption -- by preventing discovery of any match between a particular encrypted vote and its decrypted counterpart.

\pv\ accomplishes this process via a \term{mixnet}: a set of mix servers each secretly shuffle and transform, in turn, the set of encrypted votes in a verifiable way.
\pv\ is flexible enough to use either a decryption or reencryption mixnet, and with the latter, a variety of encryption schemes.
Scratch \& Vote \cite{scratch}, a variation on \pv, tallies the votes homomorphically rather than with a mixnet.

@@

Where Table R lies between encryptions and decryptions in \term{Scantegrity}, \pv\ and \term{Helios} makes use of a
cryptographic \term{mixnet} -- performed with cast ballots in hand -- to prevent an attacker from
tracing a vote to its decryption. Unlike in \term{Scantegrity}, \emph{all} encrypted votes can be traced to
their mixnet input, and \emph{all} mixnet outputs can be traced to a location in the tally; however,
those one cannot connect those two traces, such that secrecy is preserved.

@@

\pv\ provides each voter with multiple ballots, one of which she actually casts, and the others
she can audit to verify that the candidate permutation on the left-hand side corresponds to the one
encoded in the onion on the right-hand side. Audited ballots cannot be cast, but since she chooses
her actual ballot at random, if her audited ballots verify, she gains some confidence that
her real ballot would as well. Auditing authorities also verify randomly selected ballots before,
during, and after polling to garner further assurance.

Like \pv, \term{Helios} does not actually permit a voter to verify the ballot that she actually casts. Rather, it
allows users to verify a ballot without casting it (after which point it cannot be cast without
a new encryption). The assumption here is that \emph{some} voter will choose to audit a ballot, and
so the system cannot simply cheat and show the user a predetermined hash: it \emph{must} be a valid
one -- otherwise the deception would be revealed should the voter choose to exercise her right
to audit.

>>>>

\term{\pv{}} \cite{preta} also aims to offer a familiar, in-person voting experience while providing cryptographic assurance of
a fair election.

@@

The paper ballot form in \term{\pv{}} consists of two separable sides.
The left-hand side lists the candidates in permuted order.
A mark on the right-hand side in an initially empty slot adjacent to a candidate indicates a vote for that candidate.
In addition to the recorded vote, the right-hand side also includes the \term{onion}, an encryption of the ballot's particular candidate permutation.
See Figure \ref{fig:preta} for a depiction of the ballot form.

@@

Once all votes have been cast and recorded, the election authority mixes, decrypts, and tallies the votes to determine the winners while maintaining ballot secrecy.
Mixing the encrypted votes before or during the decryption process (depending on the \term{\pv{}} variant) ensures the votes remain anonymous -- even to the officials performing the encryption -- by preventing discovery of any match between a particular encrypted vote and its decrypted counterpart.

\term{\pv{}} accomplishes this process via a \term{mixnet}: a set of mix servers each secretly shuffle and transform, in turn, the set of encrypted votes in a verifiable way.
\term{\pv{}} is flexible enough to use either a decryption or reencryption mixnet, and with the latter, a variety of encryption schemes.
Scratch \& Vote \cite{scratch}, a variation on \term{\pv}, tallies the votes homomorphically rather than with a mixnet.

@@

Where Table R lies between encryptions and decryptions in \term{Scantegrity}, \term{\pv{}} and \term{Helios} makes use of a
cryptographic \term{mixnet} -- performed with cast ballots in hand -- to prevent an attacker from
tracing a vote to its decryption. Unlike in \term{Scantegrity}, \emph{all} encrypted votes can be traced to
their mixnet input, and \emph{all} mixnet outputs can be traced to a location in the tally; however,
those one cannot connect those two traces, such that secrecy is preserved.

@@

\term{\pv{}} provides each voter with multiple ballots, one of which she actually casts, and the others
she can audit to verify that the candidate permutation on the left-hand side corresponds to the one
encoded in the onion on the right-hand side. Audited ballots cannot be cast, but since she chooses
her actual ballot at random, if her audited ballots verify, she gains some confidence that
her real ballot would as well. Auditing authorities also verify randomly selected ballots before,
during, and after polling to garner further assurance.

Like \term{\pv{}}, \term{Helios} does not actually permit a voter to verify the ballot that she actually casts. Rather, it
allows users to verify a ballot without casting it (after which point it cannot be cast without
a new encryption). The assumption here is that \emph{some} voter will choose to audit a ballot, and
so the system cannot simply cheat and show the user a predetermined hash: it \emph{must} be a valid
one -- otherwise the deception would be revealed should the voter choose to exercise her right
to audit.
